\begin{thebibliography}{99}

\bibitem{mining}
Lee, Wenke, Salvatore J. Stolfo, and Kui W. Mok. "A data mining framework for building intrusion detection models." Security and Privacy, 1999. Proceedings of the 1999 IEEE Symposium on. IEEE, 1999.

\bibitem{ripper}
Cohen, William W. "Fast effective rule induction." ICML. Vol. 95. 1995.

\bibitem{cluster}
Portnoy, Leonid, Eleazar Eskin, and Sal Stolfo. "Intrusion detection with unlabeled data using clustering." In Proceedings of ACM CSS Workshop on Data Mining Applied to Security (DMSA-2001. 2001.

\bibitem{httplearn}
Kruegel, Christopher, Giovanni Vigna, and William Robertson. "A multi-model approach to the detection of web-based attacks." Computer Networks 48.5 (2005): 717-738.

\bibitem{botcraft}
Gianvecchio, Steven, et al. "Battle of Botcraft: fighting bots in online games with human observational proofs." Proceedings of the 16th ACM conference on Computer and communications security. ACM, 2009.

\bibitem{gamep2p}
Xiang-bin, Shi, et al. "A cheating detection mechanism based on fuzzy reputation management of P2P MMOGs." Software Engineering, Artificial Intelligence, Networking, and Parallel/Distributed Computing, 2007. SNPD 2007. Eighth ACIS International Conference on. Vol. 2. IEEE, 2007.

\bibitem{gamefps}
Laurens, Peter, et al. "A novel approach to the detection of cheating in multiplayer online games." Engineering Complex Computer Systems, 2007. 12th IEEE International Conference on. IEEE, 2007.

\bibitem{ghostrouter}
GHOSTROUTER. http://www.internal.co.jp/products/util/ghostrouter/about/

\bibitem{django}
Django project. https://www.djangoproject.com

\bibitem{python}
Python programming language. http://www.python.org

\bibitem{clf}
Log format. Apache. http://httpd.apache.org/docs/2.4/mod/mod\_log\_config.html

\bibitem{pickle}
Pickle. Python. http://docs.python.jp/2/library/pickle.html

\bibitem{dbscan}
Ester, Martin, et al. "A density-based algorithm for discovering clusters in large spatial databases with noise." KDD. Vol. 96. 1996.

\bibitem{cheatclass}
Yan, Jeff, and Brian Randell. "A systematic classification of cheating in online games." Proceedings of 4th ACM SIGCOMM workshop on Network and system support for games. ACM, 2005.

\bibitem{kmean}
Hartigan, John A. Clustering algorithms. John Wiley \& Sons, Inc., 1975.

\bibitem{sklearn}
Pedregosa, Fabian, et al. "Scikit-learn: Machine learning in Python." The Journal of Machine Learning Research 12 (2011): 2825-2830.

\bibitem{weka}
Hall, Mark, et al. "The WEKA data mining software: an update." ACM SIGKDD Explorations Newsletter 11.1 (2009): 10-18.

\end{thebibliography}
